Capital Budget Funding in Toronto

### 2024-09-26 paper/paper.qmd
small formatting changes to yearly funding graph in quarto
Improved abstract

---
title: "Capital Budget Funding in Toronto"
subtitle: "An Analysis of the Funding Disparties Across Toronto Wards (2022 - 2031)"
author: 
  - Maria Mangru 
thanks: "Code and data are available at: https://github.com/MariaMangru/Capital-Budget-Allocations-and-Median-Household-Income."
date: today
date-format: long
abstract: "This research examines the allocation of capital funding across Toronto's 25 wards and explores how these allocations correspond with various socioeconomic indicators. The analysis reveals significant disparities in per capita funding, with higher-income wards often receiving more funding than lower-income wards."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Lots of tables and graphs to be included here once they're properly formatted!

>>>>

---
title: "Capital Budget Funding in Toronto"
subtitle: "An Analysis of the Funding Disparties Across Toronto Wards (2022 - 2031)"
author: 
  - Maria Mangru 
thanks: "Code and data are available at: https://github.com/MariaMangru/Capital-Budget-Allocations-and-Median-Household-Income."
date: today
date-format: long
abstract: "This research examines the allocation of capital funding across Toronto's 25 wards from 2022 to 2031, examining its relationship with socioeconomic indicators. The results reveal significant disparities in per capita funding, with higher-income wards and those with higher educational attainment receiving disproportionately more investment. Conversely, wards with higher proportions of low-income households and visible minority populations receive less funding per capita."
format: pdf
number-sections: true
bibliography: references.bib
---

@@
